thesis2024

### 2025-05-06 02-creating-frames.qmd
Mac work session. Improved project .qmd structure for final render prep

knitr::include_graphics(here::here("figures/creating-frames/map_layout.png"))

@@

knitr::include_graphics(here::here("figures/creating-frames/fieldwork.png"))

@@

petrolist <- read_csv(here::here("data/raw_data_frames/petro_sample.csv"))
knitr::kable(petrolist) |> 
  kable_styling(latex_options = c("striped", "scale_down", "repeat_header"))

@@

knitr::include_graphics(here::here("figures/creating-frames/sources_map.png"))

@@

outcrop_db <- read_csv(here::here("data/raw_data_frames/outcrop_short.csv"))

@@

knitr::include_graphics(here::here("figures/creating-frames/macro_lowerJ_west.png"))

@@

knitr::include_graphics(here::here("figures/creating-frames/lowerJ_west.png"))

@@

knitr::include_graphics(here::here("figures/creating-frames/upperJ_west.png"))

@@

knitr::include_graphics(here::here("figures/creating-frames/middleJ_east.png"))

@@

knitr::include_graphics(here::here("figures/creating-frames/upperJ_east.png"))

@@

knitr::include_graphics(here::here("figures/creating-frames/macro_comparison.png"))

>>>>

knitr::include_graphics(here::here("data/creating-frames/map_layout.png"))

@@

knitr::include_graphics(here::here("data/creating-frames/fieldwork.png"))

@@

petrolist <- read_csv(here::here("data/creating-frames/petro_sample.csv"))
knitr::kable(petrolist) |> 
  kable_styling(latex_options = c("striped", "scale_down", "repeat_header"))

@@

knitr::include_graphics(here::here("data/creating-frames/sources_map.png"))

@@

outcrop_db <- read_csv(here::here("data/creating-frames/outcrop_short.csv"))

@@

knitr::include_graphics(here::here("data/creating-frames/macro_lowerJ_west.png"))

@@

knitr::include_graphics(here::here("data/creating-frames/lowerJ_west.png"))

@@

knitr::include_graphics(here::here("data/creating-frames/upperJ_west.png"))

@@

knitr::include_graphics(here::here("data/creating-frames/middleJ_east.png"))

@@

knitr::include_graphics(here::here("data/creating-frames/upperJ_east.png"))

@@

knitr::include_graphics(here::here("data/creating-frames/macro_comparison.png"))
